Radioastronomical image reconstruction using Kalman filter under ionospheric perturbations

### 2022-08-07 article/article.tex
update article

	Those distant objects are not fixed in time and a lot of calculations have been done to create evolution models for them. The objective here is not to use observations to confirm models, but to assume a model is known and get better results from the knowledge of observations and model.

		A Kalman filter is a linear quadratic estimator, using observations, state-transition model and knowledge about noise and errors to compute a more accurate result than observations alone. Radio astronomical measures being prone to noise and errors, usage of this filtering method seems \emph{a priori} a good way to improve accuracy of reconstruction. \\
		One objective of this paper is to evaluate if measure conditions and results are compatible with the filtering.

@@

@@

	Data simulation will be done as stated in [REF TER]. First the visibilities matrix is computed using the reference image and the UV-plane of the antenna mesh. To simulate visibilities at different snapshots, we apply the wanted transformation without noise and use the same UV-plane matrix to compute visibilities.\\

@@

	When reviewing Kalman filter performances under real conditions, the reference image is not considered as knwon, and we need to reconstruct the image from the visibilities matrix. While different methods exist [REF TER], the ones used here are MVDR reconstructions followed by Maximum Entropy deconvolution.

@@

>>>>

	Those distant objects are not fixed in time and a lot of calculations have been done to create evolution models for them. The goal here is not to use observations to confirm models, but to assume a model is known and get better results considering the knowledge of both observations and model. \\

	A (non extended) Kalman filter is a linear quadratic estimator, using observations, state-transition model and knowledge about noise and errors to compute a more accurate result than observations alone. Radio astronomical measures being prone to noise and errors, usage of this filtering method seems \emph{a priori} a good way to improve accuracy of reconstruction. \\

	A sensitive part of the filter is the observations model, needing precise knowledge of antennas positions and directions. An objective of this work is to determine how inaccuracies in these measurements affect image reconstruction, and if it is realistically usable in radio astronomical imagery. \\

@@

	SATIE stands for \emph{laboratoire des Systèmes et Applications des Technologies de l'Information et de l'Energie} (Information and Energy Technology Systems and Applications Laboratory).\\
	Created in 1975 under the name \emph{Laboratoire d'Electricité de l'ENSET}, then renamed \emph{LESiR} in 1984 at the time of its association with CNRS, then finally SATIE in 2002, the laboratory studies

@@

	Data simulation will be done as stated in \cite{TER}. First the visibilities matrix is computed using the reference image and the UV-plane of the antenna mesh. To simulate visibilities at different snapshots, we apply the wanted transformation without noise and use the same UV-plane matrix to compute visibilities.\\

@@

	When reviewing Kalman filter performances under real conditions, the reference image is not considered as knwon, and we need to reconstruct the image from the visibilities matrix. While different methods exist \cite{TER}, the ones used here are MVDR reconstructions followed by Maximum Entropy deconvolution.

@@

	\paragraph{Directional error on one antenna :} on larger arrays, ionospheric perturbations might not affect all antennas the same, thus studying the reliability when one antenna has errors might be an idea to explore.

	\paragraph{Use of smoothers :} when using a Kalman filter, only prior knowledge of data is needed. When all measures at different snapshots are done, a \emph{smoother}\cite{RTS} can be used to give better Kalman results, their reliability under perturbations needs to be discussed.

	\paragraph{Deep learning :} In image processing, deep learning and artificial intelligence are getting more effective and reliable. In particular, model based deep learning \cite{deep} can be an effective way of rebuilding images when an evolution model is known.
